Type Refinements for the Working Class

### 2015-11-13 paper.tex
Change arrow styles
Fix up another arrow
Cite Taylor; rename π_W to π

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can deploy
a generic logical framework. Recall from \cite{sterling-morrison:2015} that
$\SCtx$ is the category of symbol-contexts and their injective, sort-preserving
renamings. Then, fix a small category $\mathcal{W}$ of worlds along with a map
$\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ (sometimes with $\mathcal{W}$
omitted) such that $\pi_\mathcal{W}$ is a Grothendieck
fibration~\cite{jacobs:2001}:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&, row sep = large]
    {\IMode{\mathcal{W}}}
      \arrow[dash, d]
    \&
    {\IMode{{w}_{i}}}
      \arrow[drrr]
      \arrow[dr, dotted]
      \arrow[dd]
    \&
    {}\&
    {}\&
    {}\\
    {\IMode{{\pi}}}
      \arrow[d]
    \&
    {}\&
    {\OMode{{w}_{j}}}
      \arrow[rr, swap, "\OMode{{\iota}_{\varrho}}"]
      \arrow[dd, bend right = 50]
      \arrow[d]
    \&
    {}\&
    |[alias = Wk]|{\IMode{{w}_{k}}}
      \arrow[d]
    \\
    {\IMode{\SCtx}}\&
    |[alias = Ui]|{\IMode{{\Upsilon}_{i}}}
      \arrow[dr]
    \&
    {\OMode{\scriptstyle{{\pi}({w}_{j})}}}
      \arrow[rr, "\OMode{{\pi}({\iota}_{\varrho})}", ""{name = Msrc, swap}]
      \arrow[equals, d]
    \&
    {}\&
    {\IMode{\scriptstyle{{\pi}({w}_{k})}}}
      \arrow[equals, d]
    \\
    {}\&
    {}\&
    {\IMode{{\Upsilon}_{j}}}
      \arrow[rr, swap, "{\IMode{\varrho}}", ""{name = Mtgt, swap}]
    \&
    {}\&
    |[alias = Uk]|{\IMode{{\Upsilon}_{k}}}
    \arrow[from = Wk, to = Uk, bend right = 50, crossing over]
    \arrow[equals, from = Msrc, to = Mtgt]
    \arrow[from = Ui, to = Uk, crossing over]
  \end{tikzcd}
\]
Then, a \emph{judgment} shall be interpreted as an object in the presheaf
category $\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a
judgment is identified with the intensional set of its renaming-sensitive
derivations.

>>>>

\tikzset{
   commutative diagrams/.cd,
   arrow style = tikz,
   diagrams={>=latex}
}

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can deploy
a generic logical framework. Recall from \cite{sterling-morrison:2015} that
$\SCtx$ is the category of symbol-contexts and their injective, sort-preserving
renamings. Then, fix a small category $\mathcal{W}$ of worlds along with a map
$\Of{\pi}{\mathcal{W}\to\SCtx}$ such that $\pi$ is a Grothendieck
fibration~\cite{jacobs:2001, taylor:1999}:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&, row sep = large]
    {\IMode{\mathcal{W}}}
      \arrow[dash, d]
    \&
    {\IMode{{w}_{i}}}
      \arrow[drrr]
      \arrow[dotted, dr]
      \arrow[mapsto, dd]
    \&
    {}\&
    {}\&
    {}\\
    {\IMode{{\pi}}}
      \arrow[d]
    \&
    {}\&
    {\OMode{{w}_{j}}}
      \arrow[rr, swap, "\OMode{{\iota}_{\varrho}}"]
      \arrow[mapsto, dd, bend right = 50]
      \arrow[mapsto, d]
    \&
    {}\&
    |[alias = Wk]|{\IMode{{w}_{k}}}
      \arrow[mapsto, d]
    \\
    {\IMode{\SCtx}}\&
    |[alias = Ui]|{\IMode{{\Upsilon}_{i}}}
      \arrow[dr]
    \&
    {\OMode{\scriptstyle{{\pi}({w}_{j})}}}
      \arrow[rr, "\OMode{{\pi}({\iota}_{\varrho})}", ""{name = Msrc, swap}]
      \arrow[equals, d]
    \&
    {}\&
    {\IMode{\scriptstyle{{\pi}({w}_{k})}}}
      \arrow[equals, d]
    \\
    {}\&
    {}\&
    {\IMode{{\Upsilon}_{j}}}
      \arrow[rr, swap, "{\IMode{\varrho}}", ""{name = Mtgt, swap}]
    \&
    {}\&
    |[alias = Uk]|{\IMode{{\Upsilon}_{k}}}
    \arrow[mapsto, from = Wk, to = Uk, bend right = 50, crossing over]
    \arrow[equals, from = Msrc, to = Mtgt]
    \arrow[from = Ui, to = Uk, crossing over]
  \end{tikzcd}
\]
Then, a \emph{judgment} shall be interpreted as an object in the presheaf
category $\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a
judgment is identified with the intensional set of its renaming-sensitive
derivations.
